---
title: "Leakage-Controlled Prediction in Private Markets"
format: html
execute:
  echo: true
  warning: false
  message: false
---

## Purpose

This is the R companion wrapper for the canonical Python Chapter 9 public
implementation. `sample` is the default public mode. `live` rerenders the
chapter-facing figures from proprietary local inputs outside `repo/`.

```{r}
data_mode <- "sample"    # "sample" or "live"
live_data_dir <- ""      # optional override for live mode
```

```{r}
library(glue)

this_dir <- normalizePath(getwd(), winslash = "/", mustWork = TRUE)
chapter_root <- normalizePath(file.path(this_dir, ".."), winslash = "/", mustWork = TRUE)
python_dir <- normalizePath(file.path(chapter_root, "python"), winslash = "/", mustWork = TRUE)
runner_path <- normalizePath(file.path(python_dir, "run_vc_pe_exit_prediction.py"), winslash = "/", mustWork = TRUE)
output_dir <- normalizePath(
  file.path(this_dir, if (data_mode == "sample") "rendered-sample" else "rendered-live"),
  winslash = "/",
  mustWork = FALSE
)
dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)

args <- c(
  shQuote(runner_path),
  "--data-mode", data_mode,
  "--outdir", shQuote(output_dir)
)
if (nzchar(live_data_dir)) {
  args <- c(args, "--live-data-dir", shQuote(live_data_dir))
}
command <- glue("python {paste(args, collapse = ' ')}")
status <- system(command)
if (!identical(status, 0L)) {
  stop(glue("Chapter 9 Python companion run failed with exit code {status}."))
}
cat(glue("Chapter 9 figure package written to: {output_dir}\n"))
```

The code directory retains the original `VC & PE Exit Prediction` folder name for backward compatibility with existing repository paths; the manuscript title is now `Leakage-Controlled Prediction in Private Markets`.
